Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
Add brief cause of qui section

\subsection{Full Sample}\label{ssec:fullsamp}

A version of Figure~\ref{fig:fig1} for the rest of the subhalos in our original sample are given in the Appendix. They display a variety of morphologies, likely arising from a similar variety of processes. They are the subject of continuing work.

>>>>

\subsection{Cause of Quiescence}\label{ssec:cause_qui}
It is natural to question why the minimum in the SFR occurs. In \citet{2024arXiv240707985B}, AGN activity from a merger was the suspected cause. Here, we can see that there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}). Establishing a causal relationship between the two is beyond the scope of the present work, though it is the same suspected cause as in \citet{2024arXiv240707985B}.

% \subsection{Full Sample}\label{ssec:fullsamp}
